
Matlab code was used to generate the plots shown next (see \controlbookurl{http://controlbook.byu.edu} for Matlab code). However, Python code that has similar functionality is also shown below.

\lstinputlisting[language=Python, caption=armParamHW17.py]{../control_book_public_solutions/_a_arm/python/hw17/armParamHW17.py}

%\begin{lstlisting}
%% transfer functions for plant and controller
%Plant = tf([2/P.m/P.ell^2],
%           [1, 2*P.b/P.m/P.ell^2, 0]);
%C_pid = tf([(P.kd+P.kp*P.sigma),
%            (P.kp+P.ki*P.sigma),P.ki],...
%           [P.sigma,1,0]);
%
%% margin and bode plots for PID control
%figure(1), clf, margin(Plant*C_pid), 
%	grid on, hold on
%bode(Plant*C_pid/(1+Plant*C_pid)) 
%legend('Open Loop', 'Closed Loop')
%\end{lstlisting}

The transfer function for the plant is defined in Line~13.  The transfer function for the PID controller is
\begin{align*}
C_{PID}(s) &= k_P + \frac{k_I}{s} + \frac{k_D s}{\sigma s + 1} 
           = \frac{s(\sigma s+1)k_P + (\sigma s + 1)k_I + k_D s^2}{s(\sigma s + 1)} \\
           &= \frac{(k_D+\sigma k_P)s^2 + (k_P+\sigma k_I)s + k_I}{s(\sigma s + 1)},
\end{align*}
and is defined in Line~18-19.  The {\tt margin} command is similar to the {\tt bode} command except that it also annotates the Bode plot with the phase and gain margins. The results of similar code from Matlab are shown in \fref{fig:hw_arm_margins}.
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_arm_margins}
	{The {\tt margin} plot of the open loop system and the {\tt bode} plot of the closed loop system, of the single link robot arm under PID control.}
	{fig:hw_arm_margins}
As seen in \fref{fig:hw_arm_margins} the bandwidth for PID control is approximately $10$~rad/sec, which is slightly larger than the cross over frequency of $6.21$~rad/sec.  The larger bandwidth is due to the small phase margin of $PM=45.6$~degrees.

